Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2016-03-17 paper.tex
Standardized year
Filled in numbers

The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.77}$
for the low-redshift
dust-poor galaxies.  If we use the IR and UV luminosities from
\citealt{overzier11}, \alephha~= \alephuv$^{XXXX}$.  We lack
uncertainties on any SFRs so we also perform a robust linear regression,
which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv.  It
returns a similar result, as does a bootstrap resampling.  We recover a relation
close to the
\citet{calzetti97b} relation for similar galaxies, so we have some confidence
that our procedure is grossly correct.  We stress, again, that there are
no evolutionary connections between the low- and high-redshift galaxy samples;
we aim only to reproduce the \citet{calzetti97b} result with our nonstandard
method of determining \alephha.

@@

The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.54}$ for high-redshift
dusty galaxies.  We leave limits out of this fit.  The uncertainty in
the index is very small; this is not surprising given the number of galaxies.
The dispersion about the best-fit relation is large; the central 50\% of
galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{XXXX}$
and \alephha~= \alephuv$^{XXXX}$.  A survival regression, which incorporates
H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
$q\,\log\,$\alephuv, finds $q = XXXX$, as does a simple linear regression using
only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
the UV and H$\alpha$ SFRs.  The main effect of including limits in the
regression is to increase the standard error of the sample's best-fit index; a
marginally different index is a secondary effect.  Table \ref{regress}
summarizes the relevant quantities for the main fit to each sample of galaxies.

\begin{deluxetable}{lllll}
\tablecolumns{5}
\tablewidth{0pc}
\tablecaption{Summary of regressions\label{regress}}
\tablehead{
\colhead{Sample} &
\colhead{$q$} &
\colhead{Std. error of $q$} &
\colhead{Residual std. error} &
\colhead{DOF}
}
\startdata
Low-z dust-poor & 0.766 & XXXX & XXXX & XXXX \\
Low-z dusty     & 0.532 & XXXX & XXXX & XXXX \\
High-z dusty    & 0.537 & XXXX & XXXX  & XXXX
\enddata
\end{deluxetable}

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's SFR has been
constant for at least 415 Myr.  For example, if most
massive stars formed over 15 Myr instead of 415 Myr, we should multiply
$0.16 \times L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 56\% higher and the true IR SFR is 60\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
could contribute to a given escape fraction.  The spread is imprecise for two
reasons:
\begin{enumerate}
\item We define the UV escape fraction as a function of UV- and IR-derived SFRs.
\citet{madau14} use the models of \citet{conroy10} to calculate
conversion factors between luminosities and SFRs.  The
conversion factor between $L_{\mathrm{IR}}$ and
IR-derived SFR is a function of the UV escape fraction as well as the duration
of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We set aside the
circularity that results from using both these functions by fixing the UV
escape fraction in the SFR(IR)/$L_{\mathrm{IR}}$ function to the
given UV escape fraction.
\item Since SFR(IR)/$L_{\mathrm{IR}}$ is a function of more than duration of the
star formation episode, at a duration of 415 Myr most of the IR
conversion factors differ from our adopted value in \S\ref{sfrs}.
\end{enumerate}
Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

We perform a second experiment to investigate the effect of episodes of constant
star formation rate with variable duration on the dispersion about the best-fit
relation.  For each high-redshift dusty galaxy we draw a random duration from a
uniform distribution with limits at 20 Myr and 15 Gyr.  We calculate the
galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
The IR conversion factor requires a UV escape fraction from one of the given
UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
fraction which is closest to the galaxy's UV escape fraction for a duration
of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
escape fractions for the random duration.  We perform a regression for the
sample of galaxies, record $q$, and repeat the process 10,000 times.  Fig.
\ref{} shows the distribution of $q$ values from this process.  While the
$q$ values bounding the central 50\% of the sample encompass the range of $q$
values in Fig. \ref{}, we caution that this simulation involves many
assumptions.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{spread_hauv_age.eps}
\caption{The spread of true escape fractions that could contribute to
a given escape fraction if a galaxy's SFR has been constant for a
duration different from 415 Myr.  We assign the input
$f_{\mathrm{esc}}$ values to the conversion factors
between luminosities and SFRs in \S\ref{sfrs}.  The UV and IR conversion
factors change as the duration of the star formation episode varies \citep{madau14}.
The durations for the points shown here range from $2\times10^{7}$ to
$1.5\times10^{10}$ yr.\label{spread}}
\end{figure}

>>>>

The top left panel of Fig. \ref{fha_fuv} shows that \alephha~= \alephuv$^{0.77}$
for the low-redshift
dust-poor galaxies.  If we use the IR and UV luminosities from
\citealt{overzier11}, \alephha~= \alephuv$^{0.80}$.  We lack
uncertainties on any SFRs so we also perform a robust linear regression,
which requires a fit to the form $\log\,$\alephha~= $q\,\log\,$\alephuv.  It
returns a similar result, as does a bootstrap resampling.  We recover a relation
close to the
\citet{calzetti97b} relation for similar galaxies, so we have some confidence
that our procedure is grossly correct.  We stress, again, that there are
no evolutionary connections between the low- and high-redshift galaxy samples;
we aim only to reproduce the \citet{calzetti97b} result with our nonstandard
method of determining \alephha.

@@

The bottom left panel of Fig. \ref{fha_fuv} shows that \alephha~=
\alephuv$^{0.54}$ for high-redshift
dusty galaxies.  We leave limits out of this fit.  The uncertainty in
the index is very small; this is not surprising given the number of galaxies.
The dispersion about the best-fit relation is large; the central 50\% of
galaxies with H$\alpha$-detected SFRs lies between \alephha~= \alephuv$^{0.44}$
and \alephha~= \alephuv$^{0.63}$.  A survival regression, which incorporates
H$\alpha$ SFR limits in a fit to the form $\log\,$\alephha~=
$q\,\log\,$\alephuv, finds $q = 0.46$, as does a simple linear regression using
only the H$\alpha$-detected SFRs.  None of the galaxies have limits for both
the UV and H$\alpha$ SFRs.  The main effect of including limits in the
regression is to increase the standard error of the sample's best-fit index; a
marginally different index is a secondary effect.  Table \ref{regress}
summarizes the relevant quantities for the main fit to each sample of galaxies.

\begin{deluxetable}{lllll}
\tablecolumns{5}
\tablewidth{0pc}
\tablecaption{Summary of regressions\label{regress}}
\tablehead{
\colhead{Sample} &
\colhead{$q$} &
\colhead{Std. error of $q$} &
\colhead{Residual std. error} &
\colhead{DOF}
}
\startdata
Low-z dust-poor & 0.766 & 0.091 & 6.1 & 13 \\
Low-z dusty     & 0.532 & 0.027 & 65.0 & 54 \\
High-z dusty    & 0.537 & 0.008 & 6.5 & 320
\enddata
\end{deluxetable}

@@

The dispersion about the best-fit relation for high-redshift dusty galaxies
is large, yet it is susceptible
to our possibly invalid assumption that a galaxy's SFR has been
constant for at least 415 Myr.  For example, if most
massive stars formed over 15 Myr instead of 415 Myr, we should multiply
$0.16 \times L_{0.16}$ and $L_{\mathrm{IR}}$ by larger numbers than we do here to derive the
UV and IR SFRs.  The true UV SFR is 56\% higher and the true IR SFR is 60\%
higher \citep{madau14}.  The true UV escape fraction is little different;
because the true total SFR is higher, the true H$\alpha$ escape fraction is
lower.  Fig. \ref{spread} exemplifies the spread of true escape fractions that
could contribute to a given escape fraction.  The spread is imprecise for two
reasons:
\begin{enumerate}
\item We define the UV escape fraction as a function of UV- and IR-derived SFRs.
\citet{madau14} use the models of \citet{conroy10} to calculate
conversion factors between luminosities and SFRs.  The
conversion factor between $L_{\mathrm{IR}}$ and
IR-derived SFR is a function of the UV escape fraction as well as the duration
of the star formation episode: SFR(IR)/$L_{\mathrm{IR}} = \mathrm{function}
[\mathrm{duration}, f_{\mathrm{esc}}(0.16\,\micron)]$.  We set aside the
circularity that results from using both these functions by fixing the UV
escape fraction in the SFR(IR)/$L_{\mathrm{IR}}$ function to the
given UV escape fraction.
\item Since SFR(IR)/$L_{\mathrm{IR}}$ is a function of more than duration of the
star formation episode, at a duration of 415 Myr most of the IR
conversion factors differ from the value we adopt in \S\ref{sfrs}.
\end{enumerate}
Another scenario is that massive stars stopped forming within the last
15 Myr.  Perhaps some of the high-redshift dusty galaxies have
complicated star formation histories; the combined effect of deriving correct
SFRs might lead to lower dispersion.

We perform a second test to investigate the effect of episodes of constant
star formation rate with variable duration on the dispersion about the best-fit
relation.  For each high-redshift dusty galaxy we draw a random duration from a
uniform distribution with limits at 20 Myr and 2 Gyr.  We calculate the
galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
The IR conversion factor requires a UV escape fraction from one of the given
UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
fraction which is closest to the galaxy's UV escape fraction for a duration
of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
escape fractions for the random duration.  We perform a regression for the
sample of galaxies, record $q$, and repeat the process 10,000 times.  Fig.
\ref{} shows the distribution of $q$ values from this process.  While the
$q$ values bounding the central 50\% of the sample encompass the range of $q$
values in Fig. \ref{}, we caution that our assumption of a uniform distribution
of durations is likely incorrect.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{spread_hauv_age.eps}
\caption{The spread of true escape fractions that could contribute to
a given escape fraction if a galaxy's SFR has been constant for a
duration different from 415 Myr.  We assign the input
$f_{\mathrm{esc}}$ values to the conversion factors
between luminosities and SFRs in \S\ref{sfrs}.  The UV and IR conversion
factors change as the duration of the star formation episode varies \citep{madau14}.
The durations for the points shown here range from 20 Myr to
2 Gyr.\label{spread}}
\end{figure}
